Parallel Programming in Haskell Almost for Free

### 2013-11-12 src2/embarbb/programming.tex
update

The matrix-vector multiplication code above is very concise, but some further
steps are necessary before it can be run on real data. The code 
below shows how to set up a 4x4 scaling matrix and a vector to 
multiply by that matrix using ArBB. This entails allocating 
memory on the ArBB heap and copying data into it, reminiscent of the copying of
data from
host to 
device that is common in general purpose GPU (GPGPU) programming .

%[samepage=true] 
\begin{Verbatim} 
int main(void)
{
  float matrix[4][4] = {{2.0,0.0,0.0,0.0},
                        {0.0,2.0,0.0,0.0},
                        {0.0,0.0,2.0,0.0},
                        {0.0,0.0,0.0,2.0}};
  float vector[4] = {1.0,2.0,3.0,4.0};

@@

  return 0;
}
\end{Verbatim}

>>>>

The matrix-vector multiplication code above is very concise, but some further
steps are necessary before it can be run on real data. The code 
in figure~\ref{fig:EMB_ARBBFIG} shows how to set up a 4x4 scaling matrix and a vector to 
multiply by that matrix using ArBB. This entails allocating 
memory on the ArBB heap and copying data into it, reminiscent of the copying of
data from
host to 
device that is common in general purpose GPU (GPGPU) programming . 
\begin{figure}
\begin{small}
\begin{Verbatim} [samepage=true] 
int main(void)
{
  float matrix[4][4] = {{2.0,0.0,0.0,0.0},
                        {0.0,2.0,0.0,0.0},
                        {0.0,0.0,2.0,0.0},
                        {0.0,0.0,0.0,2.0}};
  float vector[4] = {1.0,2.0,3.0,4.0};

@@

  return 0;
}
\end{Verbatim}
\end{small}

\caption{ArBB glue code.}
\label{fig:EMB_ARBBFIG}

\end{figure}
